Placeholder

### 2021-02-06 Paper_Histograms.Rmd
Added chunks to get positive depression and anxiety diagnosis bu sample cohort

@@

dat.retro_diagnosis_sums <- data.frame(apply(dat.retro[c("depressive_disorders_numeric", "anxiety_disorders_numeric", "eating_disorders_numeric", "obsessive_compulsive_disorders_numeric", "psychotic_disorders_numeric", "autism_spectrum_disorder_numeric", "mhd.attention_deficit_hyperactivity_disorder_numeric", "personality_cluster_a_numeric", "personality_cluster_b_numeric", "personality_cluster_c_numeric", "mhd.mania_hypomania_bipolar_or_manicdepression_numeric", "mhd.posttraumatic_stress_disorder_ptsd_numeric", "control_numeric")],2,table))

dat.retro_diagnosis_variables <- data.frame(c("depressive disorders", "anxiety disorders", "eating disorders", "OCDs", "psychotic disorders", "aSD", "ADHD", "personality cluster a", "personality cluster b", "personality cluster c", "mania hypomania bipolar or manicdepression", "PTSD", "control"))

dat.retro_positive_diagnosis <- data.frame(t(dat.retro_diagnosis_sums[2,]))

dat.retro_diagnosis_type <- cbind(dat.retro_diagnosis_variables, dat.retro_positive_diagnosis)

names(dat.retro_diagnosis_type) <- c("diagnosis", "count")

@@

>>>>

```{r Get MDD positive total}

dat.retro_mdd_by_sample <- dat.retro %>%
  group_by(Sample_plot) %>% 
  select(depressive_disorders_numeric) %>% 
  filter(depressive_disorders_numeric == 1)

dat.retro_mdd_by_sample %>% 
  group_by(Sample_plot) %>% 
  summarise(mdd_total = n())

```{r Get anxiety positive total}

dat.retro_anxi_by_sample <- dat.retro %>%
  group_by(Sample_plot) %>% 
  select(anxiety_disorders_numeric) %>% 
  filter(anxiety_disorders_numeric == 1)

dat.retro_anxi_by_sample <- dat.retro_anxi_by_sample %>% 
  group_by(Sample_plot) %>% 
  summarise(anxi_total = n())

@@

#dat.retro_diagnosis_sums <- data.frame(apply(dat.retro[c("depressive_disorders_numeric", "anxiety_disorders_numeric", "eating_disorders_numeric", "obsessive_compulsive_disorders_numeric", "psychotic_disorders_numeric", "autism_spectrum_disorder_numeric", "mhd.attention_deficit_hyperactivity_disorder_numeric", "personality_disorder_numeric", "mhd.mania_hypomania_bipolar_or_manicdepression_numeric", "mhd.posttraumatic_stress_disorder_ptsd_numeric", "control_numeric")],2,table))

#dat.retro_diagnosis_variables <- data.frame(c("depressive disorders", "anxiety disorders", "eating disorders", "OCDs", "psychotic disorders", "ASD", "ADHD", "personality disorders", "bipolar disorder", "PTSD", "control"))

#dat.retro_positive_diagnosis <- data.frame(t(dat.retro_diagnosis_sums[2,]))

#dat.retro_diagnosis_type <- cbind(dat.retro_diagnosis_variables, dat.retro_positive_diagnosis)

#names(dat.retro_diagnosis_type) <- c("diagnosis", "count")

@@

head(diamonds)
